---
title: 'HW1: Data Management'
author: "Precious Hardy"
date: "1/30/2021"
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##(1) If we wanted to test for Type I error rates, how would we do that using a simulation? [n=100]. How often would we expect to find statistically significant findings with an alpha of .05? 
```{r}
set.seed(2345)
pvs <- numeric(100)
for (i in 1:100){
  y1 <- rnorm(100, 50, 10) 
  y2 <- rnorm(100, 50, 12) 
  treatment <- rep(c("control","treatment"),each = 100)
  res <- t.test(y1, y2)
pvs[i] <- res$p.value 
}  
mean(pvs <= .05)
```
##We are likely to find statistically significant results 5% of the time.

##(2) If we wanted to see the power to detect a statistically significant correlation coefficient[n=50], how would we do that with a simulation [assume r = .30].

```{r}
cor(d1)
```


```{r}
pvs <- numeric(1000)
library(gendata)
set.seed(2512)
for (i in 1:1000){
  d1 <- genmvnorm(cor=.3, k=2, n=50)
  res <- cor.test(d1$X1, d1$X2)
  res
pvs[i] <- res$p.value
corv[i] <- res$estimate
}
mean(pvs <= .05)
```
## a. What percent of the time are p-values statistically significant?
## The p values are statistically significant 58% of the time. 

## b. Draw a basic histogram of the correlation coefficient values.

```{r} 
hist(corv, breaks = 20)
```

## c. What is the mean of the 1,000 correlation coefficients?
```{r}
mean(corv)
```
##The mean of the correlation coefficients is .30.

## d. If you had a correlation of .15 and n = 100, how much power would you have? 
```{r}
pwr::pwr.r.test(r = .15, n = 100)
```
## With a r of .15 and n=100, power would equal .32 (moderate effect).

## e. What n would you need to have power of .80 with r = .15?
```{r}
pwr::pwr.r.test(r = .15, power = .80)
```
## In order to have a power of .80, you would need roughly 346 participants (n).